### 2022-11-28 inst/Examples/Paper_results/Paper_results_2.Rmd
Minor changes
Added suppressWarnings in bremla_simulationsummarizer and small changes in the legend of a plot in Paper_results_2.Rmd

  ggl=ggplot(data.frame(x = 1,x0=1, y = 1,y0=1, rasmus=1,buizert=1,capron=1))+
    geom_line(aes(x=x,y=y,col="Synchronized onset posterior"),size=1)+
    geom_line(aes(x=x0,y=y0,col="Unsynchronized onset posterior"))+
    geom_line(aes(x=x,y=rasmus,col="Rasmussen onset"))+
    geom_line(aes(x=x,y=buizert,col="Buizert onset"))+
    geom_line(aes(x=x,y=capron,col="Capron onset"))+
                        # colour = 'Something2'), aes(x, y, fill = colour))+
  # geom_point(alpha=0, shape = 0)+ # completely transparent rectangular point 
  # scale_fill_manual(values='black', drop=FALSE) +
   # guides(color = guide_legend(override.aes = list(alpha=1, size = 1.3)))+ # showing the point in the legend
    scale_color_manual(values=c("Synchronized onset posterior"="black",
                                "Unsynchronized onset posterior"="gray",
                                "Rasmussen onset"="blue",
                                "Buizert onset"="green",
                                "Capron onset"="red"),
                       labels=c("Synchronized onset posterior",
                                "Unsynchronized onset posterior",
                                "Rasmussen onset",
                                "Buizert onset",
                                "Capron onset"))+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.5, 0.5), # move the legend to the center
        legend.title = element_blank(),
        # legend.text = element_text(size = 17),
        legend.key = element_rect(fill='NA'),
        # legend.key.size = unit(0.8,'cm'),
        panel.grid = element_blank(),
        # legend.spacing = unit(3,'cm'),
        # legend.spacing.y = unit(0.5,'cm'),
        panel.border = element_rect(colour = "white", fill='white', size=1)
  )
  ggplots[[30]] = ggl
  ggarrange(plotlist=ggplots,widths=c(6,5))

>>>>

  ggl=ggplot(data.frame(x = 1,x0=1, y = 1,y0=1, rasmus=1,buizert=1,capron=1))+
    geom_line(aes(x=x,y=y,col="Synchronized onset posterior"),size=1)+
    geom_line(aes(x=x0,y=y0,col="Unsynchronized onset posterior"))+
    geom_line(aes(x=x,y=rasmus,col="Rasmussen onset"))+
    geom_line(aes(x=x,y=buizert,col="Buizert onset"))+
    geom_line(aes(x=x,y=capron,col="Capron onset"))+
                        # colour = 'Something2'), aes(x, y, fill = colour))+
  # geom_point(alpha=0, shape = 0)+ # completely transparent rectangular point 
  # scale_fill_manual(values='black', drop=FALSE) +
   # guides(color = guide_legend(override.aes = list(alpha=1, size = 1.3)))+ # showing the point in the legend
    scale_color_manual(values=c("Synchronized onset posterior"="black",
                                "Unsynchronized onset posterior"="gray",
                                "Rasmussen et al. (2014)"="blue",
                                "Buizert et al. (2015)"="green",
                                "Capron et al. (2021)"="red"),
                       labels=c("Synchronized onset posterior",
                                "Unsynchronized onset posterior",
                                "Rasmussen et al. (2014)",
                                "Buizert et al. (2015)",
                                "Capron et al. (2021)"))+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.5, 0.5), # move the legend to the center
        legend.title = element_blank(),
        # legend.text = element_text(size = 17),
        legend.key = element_rect(fill='NA'),
        # legend.key.size = unit(0.8,'cm'),
        panel.grid = element_blank(),
        # legend.spacing = unit(3,'cm'),
        # legend.spacing.y = unit(0.5,'cm'),
        panel.border = element_rect(colour = "white", fill='white', size=1)
  )
  ggplots[[30]] = ggl
  ggarrange(plotlist=ggplots,widths=c(6,5))
